\section*{Group Management}

Business Analyst is the name of Jeremy's official role within this group project. The role includes handling the communication between the group, the supervisor and the customer. He makes sure meetings are arranged regularly, such that the supervisor and the customer are informed of the progress for the project.

Apart from the administrative tasks, he also contribute toward the development of the project. 

He has been responsible for researching relevant material for the development of the game.

Looking into aspects of strategy games such as the 4 main objectives: Explore, Exploit, Expand and Exterminate. The mechanics and balance of the Technology Tree. The stages and life cycle of a strategy game, etc.

He also researched about the topic of procedural generation for generating the map for the game. I have consulted various implementations and tested one of my own using techniques from what I have found in the material.





The Scrum methodology is employed for the project, 

It consists of a simple set of rules for its' framework that remove speculations, and unpredictability in development by progressing in bursts of short time period, known as sprint cycles. This allows for achievement of tangible results consistently, which feed back to the process as resources for future cycles. 

After the specification and requirements have been formulated for the project. The necessary components of the game were identified, creating a backlog of tasks to be accomplished for the project. They are illustrated below, where these tasks are gradually completed as development progresses with each sprint cycle. 

Backend

Frontend

Design of the website 

Game Mechanics

Map Generation

2D Sprite for tiles

Hex Grid Implementation


The period of each sprint cycle was approximately a week long, and they were managed by ... They served the role of Scrum masters who oversaw sprint cycles to make sure of progress and steer the direction of development.
 









Recovery strategies: Version control

Github is used as the version control tool for the project. This is to prevent accidental loss of progress due to any reason.






Organisation

Weekly meeting with the supervisor, Jane Sinclair, was organised and recorded on Tabula. In each meeting, new progress of development is shared and she will advise on the direction of development.

Frequent meeting between the group members also took place. This is usually at the end of sprint cycles, to discuss about any challenges encountered during implementation and what the next steps in development will be.




Meeting Minutes were 




Meeting Minutes









